Colonization-extinction dynamics determine tree species range limits in northeastern North America

### 2015-07-03 tex/manuscript.tex
Added ms support files and a bibliography

\usepackage{setspace}
\usepackage{natbib}

@@

@@

% can this apply to other organisms? animals prob not - dispersal is just too high
% this deserves a paragraph here

@@

>>>>

\usepackage{setspace}
%\usepackage{natbib}

@@

Fisichelli and colleagues reported recruitement of temperate trees into boreal ecosystems, supporting our conclusion that colonization of temperature trees varies as a function of temperature \cite{Fisichelli2014}.

@@

% can this apply to other organisms? animals prob not - dispersal is just too high
% this deserves a paragraph here
Our model is particularly appropriate for forest trees, which are sessile, disperse relatively short distances, and are long-lived. 
Unique challenges confront applying such a model without these characteristics, such as most animals. 
Animals in highly patchy environments, with local populations linked by moderate dispersal rates, are likely to be the most appropriate species for use with our model.

@@

\renewcommand\refname{Literature Cited}
\bibliography{2state}{}
\bibliographystyle{pnas}

### 2015-07-03 tex/tab_si1_col_pars.tex
Added ms support files and a bibliography

\usepackage[margin=1in]{geometry}
\usepackage{pdflscape}

@@

\multirow{2}{*}{\it Abies balsamea} & \multirow{2}{*}{MAT} & \multirow{2}{*}{MAP} & x.xx\tnote{\textsection} & x.xx & x.xx & x.xx & x.xx \\
 &  &  & {\ts (x.xx, x.xx)} & {\ts (x.xx, x.xx)} & {\ts (x.xx, x.xx)} & {\ts (x.xx, x.xx)} & {\ts (x.xx, x.xx)} \\

@@

\multirow{2}{*}{\it Acer saccharum} & \multirow{2}{*}{MAT} & \multirow{2}{*}{PS} & x.xx & x.xx & x.xx & x.xx &  \\
 &  &  & {\ts (x.xx, x.xx)} & {\ts (x.xx, x.xx)} & {\ts (x.xx, x.xx)} & {\ts (x.xx, x.xx)} &  \\

@@

\multirow{2}{*}{\it Populus tremuloides} & \multirow{2}{*}{MAT} & \multirow{2}{*}{MAP} & x.xx & x.xx & x.xx & x.xx &  \\
 &  &  & {\ts (x.xx, x.xx)} & {\ts (x.xx, x.xx)} & {\ts (x.xx, x.xx)} & {\ts (x.xx, x.xx)} &  \\

@@

\multirow{2}{*}{\it Ulmus americana} & \multirow{2}{*}{MAT} & \multirow{2}{*}{PS} & x.xx & x.xx & x.xx &  & \\
 &  &  & {\ts (x.xx, x.xx)} & {\ts (x.xx, x.xx)} & {\ts (x.xx, x.xx)} & & \\
\bottomrule
\end{tabular}
\begin{tablenotes}
\item [*] {\ts Temperature variable abbreviations: MAT: Mean annual temperature;
		MTWQ: Mean temperature wettest quarter; MDR: Mean diurnal range}
\item [\textdagger] {\ts Precipitation variable abbreviations: MAP: Mean annual precipitation; 
MPWQ: Mean precipitation, warmest quarter; PS: Precipitation seasonality}
\item [\textdaggerdbl] {\ts The parameters fit the following equation for $\gamma$, the 
		colonization rate: $log \left( \frac{\gamma}{1-\gamma} \right) = c_0 + c_1T + c_2P + c_3T^2 + c_4P^2$;
		where $T$ and $P$ are the selected temperature and precipitation variables, 
		respectively, and where a blank cell indicates a parameter that was not included 
		in the best-supported model}
\item [\textsection] {\ts Values are the median values from the posterior distribution with 5 and 95\% quantiles}
\end{tablenotes}
\end{threeparttable}
\end{table}

>>>>

\usepackage[margin=0.5in]{geometry}
\usepackage{pdflscape}

@@

\multirow{2}{*}{\it Abies balsamea} & \multirow{2}{*}{MAT} & \multirow{2}{*}{MAP} & -2.53\tnote{\textsection} & -2.46 & 0.07 & -1.26 & 0.03 \\
 &  &  & {\ts (-2.86, -2.18)} & {\ts (-3.08, -1.81)} & {\ts (-0.01, 0.16)} & {\ts (-1.55, -0.98)} & {\ts (-0.03, 0.09)} \\

@@

\multirow{2}{*}{\it Acer saccharum} & \multirow{2}{*}{MAT} & \multirow{2}{*}{PS} & -2.10 & 0.47 & 0.09 & -0.34 &  \\
 &  &  & {\ts (-2.22, -1.99)} & {\ts (0.34, 0.59)} & {\ts (0.01, 0.17)} & {\ts (-0.55, -0.12)} &  \\

@@

\multirow{2}{*}{\it Populus tremuloides} & \multirow{2}{*}{MAT} & \multirow{2}{*}{MAP} & -2.15 & -0.75 & -0.11 & -0.86 &  \\
 &  &  & {\ts (-2.44, -1.86)} & {\ts (-1.48, -0.05)} & {\ts (-0.20, -0.03)} & {\ts (-1.32, -0.43)} &  \\

@@

\multirow{2}{*}{\it Ulmus americana} & \multirow{2}{*}{MAT} & \multirow{2}{*}{PS} & x.xx & x.xx & x.xx &  & \\
 &  &  & {\ts (x.xx, x.xx)} & {\ts (x.xx, x.xx)} & {\ts (x.xx, x.xx)} & & \\
\bottomrule
\end{tabular}
\begin{tablenotes}
\item [*] {\ts Temperature variable abbreviations: MAT: Mean annual temperature;
		MTWQ: Mean temperature wettest quarter; MDR: Mean diurnal range}
\item [\textdagger] {\ts Precipitation variable abbreviations: MAP: Mean annual precipitation; 
MPWQ: Mean precipitation, warmest quarter; PS: Precipitation seasonality}
\item [\textdaggerdbl] {\ts The parameters fit the following equation for $\gamma$, the 
		colonization rate: $log \left( \frac{\gamma}{1-\gamma} \right) = c_0 + c_1T + c_2P + c_3T^2 + c_4P^2$;
		where $T$ and $P$ are the selected temperature and precipitation variables, 
		respectively, and where a blank cell indicates a parameter that was not included 
		in the best-supported model. 
		All parameters were fit to data scaled to 0 mean and unit variance.}
\item [\textsection] {\ts Values are the mean values from the posterior distribution with 5 and 95\% quantiles}
\end{tablenotes}
\end{threeparttable}
\end{table}

### 2015-07-03 tex/tab_si2_ext_pars.tex
Added ms support files and a bibliography

\multirow{2}{*}{\it Abies balsamea} & \multirow{2}{*}{MAT} & \multirow{2}{*}{MAP} & x.xx\tnote{\textsection} & x.xx & x.xx & x.xx & x.xx \\
&  &  & {\ts (x.xx, x.xx)} & {\ts (x.xx, x.xx)} & {\ts (x.xx, x.xx)} & {\ts (x.xx, x.xx)} & {\ts (x.xx, x.xx)} \\

@@

\multirow{2}{*}{\it Acer saccharum} & \multirow{2}{*}{MAT} & \multirow{2}{*}{PS} & x.xx & x.xx & x.xx & x.xx &  \\
&  &  & {\ts (x.xx, x.xx)} & {\ts (x.xx, x.xx)} & {\ts (x.xx, x.xx)} & {\ts (x.xx, x.xx)} &  \\

@@

\multirow{2}{*}{\it Populus tremuloides} & \multirow{2}{*}{MAT} & \multirow{2}{*}{MAP} & x.xx & x.xx & x.xx &  &  \\
&  &  & {\ts (x.xx, x.xx)} & {\ts (x.xx, x.xx)} & {\ts (x.xx, x.xx)} &  &  \\

@@

\multirow{2}{*}{\it Ulmus americana} & \multirow{2}{*}{MAT} & \multirow{2}{*}{PS} & x.xx & x.xx & x.xx & x.xx & \\
&  &  & {\ts (x.xx, x.xx)} & {\ts (x.xx, x.xx)} & {\ts (x.xx, x.xx)} & {\ts (x.xx, x.xx)} & \\
\bottomrule
\end{tabular}
\begin{tablenotes}
\item [*] {\ts Temperature variable abbreviations: MAT: Mean annual temperature;
		MTWQ: Mean temperature wettest quarter; MDR: Mean diurnal range}
\item [\textdagger] {\ts Precipitation variable abbreviations: MAP: Mean annual precipitation; 
MPWQ: Mean precipitation, warmest quarter; PS: Precipitation seasonality}
\item [\textdaggerdbl] {\ts The parameters fit the following equation for $\epsilon$, the 
		extinction rate: $log \left( \frac{\epsilon}{1-\epsilon} \right) = e_0 + e_1T + e_2P + e_3T^2 + e_4P^2$;
		where $T$ and $P$ are the selected temperature and precipitation variables, 
		respectively, and where a blank cell indicates a parameter that was not included 
		in the best-supported model}
\item [\textsection] {\ts Values are the median values from the posterior distribution with 5 and 95\% quantiles}
\end{tablenotes}
\end{threeparttable}
\end{table}

>>>>

\multirow{2}{*}{\it Abies balsamea} & \multirow{2}{*}{MAT} & \multirow{2}{*}{MAP} & -3.21\tnote{\textsection} & -1.55 & -0.45 & -0.98 & -0.13 \\
&  &  & {\ts (-3.56, -2.88)} & {\ts (-2.18, -0.94)} & {\ts (-0.54, -0.37)} & {\ts (-1.26, -0.70)} & {\ts (-0.19, -0.07)} \\

@@

\multirow{2}{*}{\it Acer saccharum} & \multirow{2}{*}{MAT} & \multirow{2}{*}{PS} & -3.18 & 0.73 & 0.47 & 0.32 &  \\
&  &  & {\ts (-3.32, -3.04)} & {\ts (0.61, 0.85)} & {\ts (0.39, 0.55)} & {\ts (0.08, 0.56)} &  \\

@@

\multirow{2}{*}{\it Populus tremuloides} & \multirow{2}{*}{MAT} & \multirow{2}{*}{MAP} & -1.40 & 1.20 & -0.06 &  &  \\
&  &  & {\ts (-1.56, -1.25)} & {\ts (1.02, 1.36)} & {\ts (-0.13, 0.01)} &  &  \\

@@

\multirow{2}{*}{\it Ulmus americana} & \multirow{2}{*}{MAT} & \multirow{2}{*}{PS} & x.xx & x.xx & x.xx & x.xx & \\
&  &  & {\ts (x.xx, x.xx)} & {\ts (x.xx, x.xx)} & {\ts (x.xx, x.xx)} & {\ts (x.xx, x.xx)} & \\
\bottomrule
\end{tabular}
\begin{tablenotes}
\item [*] {\ts Temperature variable abbreviations: MAT: Mean annual temperature;
		MTWQ: Mean temperature wettest quarter; MDR: Mean diurnal range}
\item [\textdagger] {\ts Precipitation variable abbreviations: MAP: Mean annual precipitation; 
MPWQ: Mean precipitation, warmest quarter; PS: Precipitation seasonality}
\item [\textdaggerdbl] {\ts The parameters fit the following equation for $\epsilon$, the 
		extinction rate: $log \left( \frac{\epsilon}{1-\epsilon} \right) = e_0 + e_1T + e_2P + e_3T^2 + e_4P^2$;
		where $T$ and $P$ are the selected temperature and precipitation variables, 
		respectively, and where a blank cell indicates a parameter that was not included 
		in the best-supported model.
		All parameters were fit to data scaled to 0 mean and unit variance.}
\item [\textsection] {\ts Values are the mean values from the posterior distribution with 5 and 95\% quantiles}
\end{tablenotes}
\end{threeparttable}
\end{table}
